Turbulence in compact to giant HII regions

### 2022-02-01 strucfunc_paper.tex
Javier changes 2022-02-01

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Sizes taken from Table 2 of \citet{1984ApJ...287..116K}. Reference from the other properties are mentioned in the text.}
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d& \text{Size,}\ S & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &   6.0      \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.8    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   22.4 \pm 2.7    \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &   31.7     \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &   10.1     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 5.7     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 7.7     \\
\bottomrule
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

The third column in Table \ref{tab:Res} shows the seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
The forth column shows the correlation value \(r_0\) in parsecs.
The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
The fifth column indicates the size of each observational box in parsecs.
The index \(m\) is shown in the last column and is commonly used as a reference for comparison between observations and the theoretic value of 0.6.
The range covered by the power-law index in our HII region sample goes from 0.7 to 1.5.
The implications of these results is further developed on the next section.

@@

A turbulent behavior in the flows is more common in fluid systems than a laminar one.
These turbulent flows tends to be unsteady, irregular and chaotic, and the turbulent motions are observed in many scales. 
The turbulent flows are associated with a high Reynolds numbers which is defined as \(Re = l v_{l} / \nu \), where \(v_{l}\) is a characteristic velocity in the fluid system and \(\nu\) is the kinematic viscosity of the medium.
Experiments have shown that a flow which is laminar become turbulent when increasing the velocity (i.e., increasing the \(Re\)) and a large range of velocity fluctuation appear at all scales.
A high \(Re\) reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones.

As astronomical observation made it possible to measure a large number of points with a high accuracy, it was found that velocities show a non-thermal component reflecting characteristic of earthly turbulent flows.
The existence of turbulent flows in astrophysical objects, ranging in scales from 10\(^6\) to 10\(^{17}\) m \citep{2010ApJ...710..853C} is thought to be consequence of the high \(Re\), between 10\(^4\) and 10\(^9\) \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.

@@

\subsection{Scaling relations between physical properties and turbulent parameters}

@@

Ideally the correlation length \(r_0\), should represent the scale of dominant energy injection. 
Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular process as the main responsible.

@@

\subsection{Projection smearing}

It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.01-0.1.

>>>>

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Sizes taken from Table 2 of \citet{1984ApJ...287..116K}. Reference from the other properties are mentioned in the text.}
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d& \text{Size,}\ S & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &   6 \pm 1      \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.8    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   22.4 \pm 2.7    \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &   31.7     \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &   10.1     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 5.7     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 7.7     \\
\bottomrule
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

The third column in Table \ref{tab:Res} shows the seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
The forth column shows the correlation value \(r_0\) in parsecs.
The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
The fifth column indicates the size of each observational box in parsecs.
The index \(m\) is shown in the last column and the range covered by the power-law index in our HII region sample goes from 0.7 to 1.5.
The implications of these results is further developed on the next section.

@@

A turbulent behavior in the flows is more common in fluid systems than a laminar one.
These turbulent flows tends to be unsteady, irregular and chaotic, and the turbulent motions are observed in many scales. 
The turbulent flows are associated with a high Reynolds numbers which is defined as \(Re = l v_{l} / \nu \), where \(v_{l}\) is a characteristic velocity in the fluid system and \(\nu\) is the kinematic viscosity of the medium.
Experiments have shown that a flow which is laminar become turbulent when increasing the velocity (i.e., increasing the \(Re\)) and a large range of velocity fluctuation appear at all scales.
A high \(Re\) reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones. 
Hence it is possible to assume that if viscosity is not dominant in a flow, this flow would be turbulent.

As astronomical observation made it possible to measure a large number of points with a high accuracy, it was found that velocities show a non-thermal component reflecting characteristic of turbulent earthly flows.
The existence of turbulent flows in astrophysical objects, ranging in scales from 10\(^6\) to 10\(^{17}\) m \citep{2010ApJ...710..853C} is thought to be consequence of the high \(Re\), between 10\(^4\) and 10\(^9\) \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.

@@

These mathematical techniques were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal} allowing to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the Orion Nebula.

\subsection{Interpretation of the turbulent parameters and origins of interstellar turbulence}\label{sec:interpretation-origin}

Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection. 
It is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates.
The main energy sources are, of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc supernova explosions inject a large amount of kinetic energy, at scales of several tens of pc the expansion of \hii{} regions is also a source of energy and bipolar flows and jets inject energy at small scales, bouth one tent of a pc.

The index \(m\) is shown in the last column of Table \ref{tab:Res} and is commonly used as a reference for comparison between observations and the theoretic value of 0.67 (equation \ref{eq:velocity-moments}).

\subsubsection{Projection smearing}\label{sec:projection-smearing}

It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02-0.1.

\subsection{Scaling relations between physical properties and turbulent parameters}\label{sec:scaling-relations}

@@

@@
